---
title: "GDP vs Life Expectancy"
author: "faeez safedien"
date: "June 30, 2018"
output: ioslides_presentation
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)
```

## Background

This is an R Markdown presentation that features a plot created with Plotly.

This project this is done as week 3 assignment for Developing Data Products Coursera’s course.

## Excecutive Summary

Using data from the gapminder library in R we graph GDP per Capita vs Life Expentancy. The size of the bubbles are proportional to the population of each country and are colour coded to represent the continent


## Interactive Graph

```{r, message=FALSE}
library(plotly)
library(gapminder)
library(plotly)
library(datasets)
gDat <- gapminder
df <- subset(gDat, year == 2007)
p <- plot_ly(df, x = ~gdpPercap, y = ~lifeExp,type ='scatter', mode = "markers" ,text= df$country, color = as.factor(df$continent), size=~pop, sizes = c(5,50), marker = list(opacicty=50,sizemode='diameter'))
layout(p, title = "Life Expectancy vs GDP per Capita" ,xaxis = list(type = "log"),
       yaxis = list(type = "log"))
```

## References
The code can be found at in my GitHub repo