---
title: "GDP vs Life Expectancy"
author: "faeez safedien"
date: "June 30, 2018"
output: ioslides_presentation
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)
```

## Background

This is an R Markdown presentation that features a plot created with Plotly.

This project this is done as week 3 assignment for Developing Data Products Coursera’s course.

## Excecutive Summary

Using data from the gapminder library in R we graph GDP per Capita vs Life Expentancy for the year 2007. The size of the bubbles are proportional to the population of each country and are colour coded to represent the continent


## Interactive Graph

```{r, message=FALSE}
library(plotly)
library(gapminder)
library(plotly)
library(datasets)
gDat <- gapminder
df <- subset(gDat, year == 2007)
p <- plot_ly(df, x = ~gdpPercap, y = ~lifeExp,type ='scatter', mode = "markers" ,hoverinfo = 'text', text= ~paste(df$country, '<br> Life Expectancy: ', df$lifeExp, 'years <br> GDP per Capita: ', round(df$gdpPercap), 'USD </br> Population: ', df$pop), color = as.factor(df$continent), size=~pop, sizes = c(5,40), marker = list(opacicty=50,sizemode='diameter'))
layout(p, title = "Life Expectancy vs GDP per Capita in 2007" ,xaxis = list(type = "log"),
       yaxis = list(type = "log"))
```

## References
The code can be found at in my [GitHub repo](https://github.com/faeezs/data-products/tree/gh-pages/week%203)